Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 results.tex
Fixed some math typesetting
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@859 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we check the effect of the \SVD\ tolerance parameter defined in
~\cite{Cannon:2010p10398}.  By changing the tolerance of the reconstruction of
the physical waveforms one effects directly the mismatch that results from the
truncation of the orthogonal filter matrix.  The conditions presented here are
more complicated than in the original work~\cite{Cannon:2010p10398} due to the
inclusion of the time sliced templates and resampling.  \FIXME{However, we find
that the results are quite as expected.}  Figure \ref{fig:hist-svd-tolerance}
demonstrates that it is possible to acheive typical \SNR\ losses of $\ll1\%$.
However, we do notice that the mismatch saturates with respect to the tolerance.
This could be the effect of the resampling, or another \SNR\ loss that we did
not model or expect.  However the saturation is still an order of magnitude below our target mismatch of $\sim 0.3 \%$.  We find that an \SVD\ tolerance of
$1-1\times10^{-4}$ is adequate. 
%
\begin{figure}
	\begin{center}
		\includegraphics{bw.pdf}
		\caption{\label{fig:hist-svd-tolerance}
Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse respones.  The \textsc{svd}
tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
The diminishing improvement is caused by some other limitation in the pipeline.}
	\end{center}
\end{figure}

@@

Next, keeping the \SVD\ tolerance fixed at $1-1\times10^{-6}$, we checked the
impact of changing the filter length used to interpolate the decimated data
back up to the full sample rate.  The results are in figure
\ref{fig:hist-interpolate}.  We find that a filter length of 16 is sufficient
to produce mismatches at our target of $\sim 0.3 \%$.
%
\begin{figure}
	\begin{center}
		\includegraphics{bw_resample.pdf}
		\caption{\label{fig:hist-interpolate} Box-and-whisker plot of
mismatch between nominal template bank and \lloid\ measured impulse respones.
The length $N^\uparrow$ of the interpolation filter is varied from 8 to 192.
The \textsc{svd} tolerance is kept fixed at $(1-10^{-6})$.  The lines in the
center of the boxes denote the medians.  The upper and lower boundaries of the
boxes show the upper and lower quartiles.  The whiskers denote the minimum and
maximum mismatch over all templates.}
	\end{center}
\end{figure}

>>>>

In this section we check the effect of the \SVD\ tolerance parameter defined in
~\cite{Cannon:2010p10398}.  By changing the tolerance of the reconstruction of
the physical waveforms one effects directly the mismatch that results from the
truncation of the orthogonal filter matrix.  The conditions presented here are
more complicated than in the original work~\cite{Cannon:2010p10398} due to the
inclusion of the time sliced templates and resampling.  \FIXME{However, we find
that the results are quite as expected.}  Figure \ref{fig:hist-svd-tolerance}
demonstrates that it is possible to acheive typical \SNR\ losses of $\ll1\%$.
However, we do notice that the mismatch saturates with respect to the tolerance.
This could be the effect of the resampling, or another \SNR\ loss that we did
not model or expect.  However the saturation is still an order of magnitude below our target mismatch of $\sim 0.3 \%$.  We find that an \SVD\ tolerance of
$\left(1-10^{-4}\right)$ is adequate. 
%
\begin{figure}
	\begin{center}
		\includegraphics{bw.pdf}
		\caption{\label{fig:hist-svd-tolerance}
Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse respones.  The \textsc{svd}
tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
The diminishing improvement is caused by some other limitation in the pipeline.}
	\end{center}
\end{figure}

@@

Next, keeping the \SVD\ tolerance fixed at $\left(1-10^{-6}\right)$, we checked the
impact of changing the filter length used to interpolate the decimated data
back up to the full sample rate.  The results are in figure
\ref{fig:hist-interpolate}.  We find that a filter length of 16 is sufficient
to produce mismatches at our target of $\sim 0.3 \%$.
%
\begin{figure}
	\begin{center}
		\includegraphics{bw_resample.pdf}
		\caption{\label{fig:hist-interpolate} Box-and-whisker plot of
mismatch between nominal template bank and \lloid\ measured impulse respones.
The length $N^\uparrow$ of the interpolation filter is varied from 8 to 192.
The \textsc{svd} tolerance is kept fixed at $(1-10^{-6})$.  The lines in the
center of the boxes denote the medians.  The upper and lower boundaries of the
boxes show the upper and lower quartiles.  The whiskers denote the minimum and
maximum mismatch over all templates.}
	\end{center}
\end{figure}
